An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-12-13 jmiv.tex
New figure in section 4

\begin{figure}[!h]
\begin{minipage}[b]{0.5\textwidth}
\center
\includegraphics[scale=0.35]{images/local_search/square-flower.eps}
\caption{Elastica computation along iterations of algorithm \ref{alg:local-search}. The final shape has energy value closer to the optimal value $2\pi/5$ (dashed line).}
\label{fig:plot-elastica-local-search}
\end{minipage}\hspace{40pt}%
\begin{minipage}[b]{0.45\textwidth}
\center
\captionsetup{type=table}
\begin{tabular}{|l|c|c|}
\hline
& $h=1.0$ & $h=0.5$\\
\hline
Square & 4s (0.4s/it) & 77s (3s/it)\\
\hline
Flower & 252s (4s/it)  & 3246s (42s/it)\\
\hline
\end{tabular}
\caption{Running times for the local combinatorial optimization algorithm with $k=1,N=50$. Four threads were used.}
\label{tab:summary-local-comb-rtime}
\end{minipage}
\end{figure}

@@

Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the goal is to evolve a flow $S^{(i)}$ where $S^{(i+1)}$ has lower digital elastica than its precedent.

We observe that the integral invariant estimator \eqref{eq:curvature_approximation} is originaly designed to be evaluated on the digital boundary of some shape, which is the unknown of our problem. Enforcing this restriction implies to incorporate topological information in the form of constraints or penalization terms in the same lines of \cite{schoenemann09linear}, but such approach would result in a third order model, which we prefer to avoid. Instead, we are going to exploit the II estimator definition in order to create a flow that evolves proportionally to the squared curvature of the current shape.

@@

@@

We remark that the minimization of \eqref{eq:energy-family} for $S^{(i)}$ is not sufficient to derive the next shape $S^{(i+1)}$ because topolical information is not included in the model. Instead, the minimization of \eqref{eq:energy-family} is used as a guide. Recall that the integral invariant estimator approaches curvature by computing the difference between half of the area
of a chosen ball and the area of the intersection of this ball with the shape.  In particular, regions of positive
curvature have fewer pixels in their intersection set than on its complement w.r.t the estimation ball. This implies
that variables in such regions are labeled with 1, as the unbalance grows otherwise. We attenuate curvature if we shift
the center of the estimation ball towards the interior of the shape, which means removing the 1-labeled pixels. That is
why we take the complement of the optimization solution.

>>>>

\begin{figure}[!h]
\begin{minipage}[b]{0.5\textwidth}
\center
\includegraphics[scale=0.35]{images/local_search/square-flower.eps}
\caption{Elastica computation along iterations of algorithm \ref{alg:local-search}. The final shape has energy value closer to the optimal value $2\pi/5$ (dashed line).}
\label{fig:plot-elastica-local-search}
\end{minipage}\hspace{40pt}%
\begin{minipage}[b]{0.45\textwidth}
\center
\captionsetup{type=table}
\begin{tabular}{|l|c|c|}
\hline
& $h=1.0$ & $h=0.5$\\
\hline
Square & 4s (0.4s/it) & 77s (3s/it)\\
\hline
Flower & 252s (4s/it)  & 3246s (42s/it)\\
\hline
\end{tabular}
\caption{Running times for the local combinatorial optimization algorithm with $k=1,n=50$. Four threads were used.}
\label{tab:summary-local-comb-rtime}
\end{minipage}
\end{figure}

@@

Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the goal is to compute a flow $S^{(i)}$ where $S^{(i+1)}$ has lower digital elastica than its precedent.

We observe that the integral invariant estimator \eqref{eq:curvature_approximation} is originaly designed to be evaluated on the digital boundary of some shape, which is the unknown of our problem. Injecting contour information leads to a third order model, which we prefer to avoid. Instead, we are going to exploit the II estimator definition in order to compute a flow that evolves proportionally to the squared curvature of the current shape.

@@

\begin{figure}
\begin{minipage}{0.5\textwidth}
\center
\includegraphics[scale=0.1]{images/flow/contour-information/before-opt.pdf}
\label{fig:contour-info-1}
\end{minipage}%
\begin{minipage}{0.5\textwidth}
\center
\includegraphics[scale=0.1]{images/flow/contour-information/after-opt.pdf}
\label{fig:contour-info-2}
\end{minipage}%
\caption{Directly using the optimization result of \eqref{eq:energy-family} doesn't decrease squared curvature because contour information is not present in the energy.}
\label{fig:contour-info}
\end{figure}

@@

We emphasize that the minimization of \eqref{eq:energy-family} for $S^{(i)}$ is not sufficient to derive the next shape $S^{(i+1)}$ because topolical information is not included in the model (see figure \ref{fig:contour-info}). Recall that the integral invariant estimator approaches curvature by computing the difference between half of the area
of a chosen ball and the area of the intersection of this ball with the shape.  In particular, regions of positive
curvature have fewer pixels in their intersection set than on its complement w.r.t the estimation ball. This implies
that variables in such regions are labeled with 1, as the unbalance grows otherwise. We attenuate curvature if we shift
the center of the estimation ball towards the interior of the shape, which means removing the 1-labeled pixels. That is
why we take the complement of the optimization solution.
